Adopting agile in the large: motivations, success factors and challenges

### 2014-01-09 journal/article.tex
Study selection process

The facet of \emph{organizational transformation} was interpreted so that the
primary study presents insights on the process of transformation. Excluded
topics were: discussing a large agile effort but not presenting the how the
organization had evolved [ref?], pilot cases that clearly span one limited
project [Scott 2008?], and case studies that provide minimal information on the
transformation process [ref?].
--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered.

@@

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. As a result we excluded the facet
\emph{large scale} from the keyword search, and relied on manual filtering.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we considered only articles including the term ``software'' or
articles published in relevant conferences. Instead of further engineering the
search terms, which proved to result in excluding some relevant articles, we
chose to manually filter the remaining search results. The resulting facets and
keywords are listed in Table \ref{table:searchterms}. The search yielded 1874
unique matches.

@@

>>>>

The facet of \emph{organizational transformation} was interpreted so that the
primary study presents insights on the process of transformation. Excluded
topics were: discussing a large agile effort but not presenting the how the
organization had evolved [ref?], pilot cases that clearly span one limited
project [Scott 2008?], and case studies that provide minimal information on the
transformation process [ref?].
--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered. [Maranzato 2012, Lyon 2008]

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. As a result we excluded the facet
\emph{large scale} from the keyword search, and relied on manual filtering.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we considered only articles including the term ``software'' or
articles published in relevant conferences. Instead of further engineering the
search terms, which proved to result in excluding some relevant articles, we
chose to manually filter the remaining search results. The resulting facets and
keywords are listed in Table \ref{table:searchterms}.

@@

The database keyword search matched 1874 unique papers. The abstracts of these
papers were categorized independently by both Dikert and Paasivaara into three
categories: include, excude, and uncertain. The result was combined by marking
abstracts both researchers agreed on for inclusion or exclusion respecitvely.
The inclusion of disagreed or uncertain abstracts was resolved through
discussion. At this stage papers were excluded only if both reserachers deemed
it clearly irrelevant, including any uncertain cases for full text filtering. As
a result 170 papers were selected for full text filtering.

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result 45 papers were selected for full text analysis. In
addition 2 papers were included from the references of the evaluated papers, and
3 papers were included from the results of the preliminary search. Finally, 50
papers were selected as primary studies.
